% Draft status: V0
% Evidence status: checked where possible; TODOs mark missing evidence.
\section{Introduction}

Object recognition has improved rapidly as visual representation learning has moved from classical convolutional networks to large-scale transformer, self-supervised, and vision-language systems. The practical question, however, is not only whether a model is accurate on average. A model deployed in geographically diverse settings may encounter familiar object labels in unfamiliar forms: different materials, household layouts, camera conditions, cultural practices, and socioeconomic contexts. In that setting, average accuracy can hide regional failure modes. A model can look strong overall while performing substantially worse for one region than another.

This paper studies that gap between benchmark progress and regional robustness. The central question is whether modern representation paradigms reduce geographic disparity, reproduce it, or reveal different versions of it when evaluated on globally diverse household-object datasets. The paper therefore treats model architecture and pretraining style as a lens for analysis rather than as a leaderboard. The evaluated models are grouped into four paradigms: the Convolutional Vision Paradigm, represented by ResNet50 and ConvNeXtV2; the Transformer Vision Paradigm, represented by DeiT3, SwinV2, and MaxViT; the Self-supervised Foundation Paradigm, represented by DINOv2 and MAE; and the Vision-Language Foundation Paradigm, represented by CLIP and SigLIP.

GeoDE and Dollar Street are appropriate datasets for this question because both were built to make geographic visual variation visible. GeoDE is a geographically diverse object-recognition dataset with images collected across six world regions \citep{ramaswamy2023geode}. Dollar Street contains household-object images from homes around the world, along with demographic metadata such as region, country, and monthly income \citep{rojas2022dollarstreet}. Prior Dollar Street work also motivates the concern that object-recognition systems may not perform uniformly across geographic and socioeconomic contexts \citep{devries2019object}. These datasets are therefore useful not merely as alternative test sets, but as probes of whether object-recognition performance is distributed evenly across regions.

Average accuracy is insufficient for this paper's question because it collapses regional behavior into a single number. If one model performs well in Europe but worse in Africa, and another model has lower average accuracy but smaller regional variation, the models pose different evaluation trade-offs. This paper therefore reports object accuracy together with per-region accuracy, worst-region accuracy, best-region accuracy, and geographic disparity. The goal is not to label one model family as fair or unfair, but to test whether the same model that improves average recognition also improves regional balance.

Comparing the four representation paradigms is meaningful because they encode different assumptions and training signals. Convolutional models emphasize locality and hierarchical feature extraction. Transformer models use attention mechanisms that can aggregate information differently across spatial positions. Self-supervised foundation models learn visual representations without ordinary supervised class labels. Vision-language foundation models align images with natural language, potentially drawing on broader semantic supervision. These differences may be associated with different regional robustness behavior, although this paper does not claim that a paradigm causes a particular disparity pattern.

The paper makes four contributions. First, it provides a controlled comparison of nine modern vision models across four representation paradigms. Second, it evaluates each model on GeoDE and Dollar Street before and after fine-tuning. Third, it analyzes average accuracy, per-region accuracy, worst-region accuracy, best-region accuracy, geographic disparity, and fine-tuning-induced changes. Fourth, it discusses how regional robustness differs from average object recognition performance and why model families should be compared using both accuracy and disparity.
