% Draft status: V0
% Evidence status: checked where possible; TODOs mark missing evidence.
\section{Related Work}

\subsection{Geographic Bias in Computer Vision}

Prior work has raised concerns that object recognition systems may not perform equally across geographic and socioeconomic contexts. \citet{devries2019object} evaluate object recognition with Dollar Street imagery and report disparities across countries and income levels. This paper builds on that motivation but uses a different empirical setup: it compares pretrained ImageNet and finetuned evaluations across two datasets and nine model families. The current draft therefore treats prior findings as motivation, not as evidence for the exact mechanisms behind the new results.

GeoDE was introduced as a geographically diverse evaluation dataset for object recognition \citep{ramaswamy2023geode}. It is directly relevant because this paper uses GeoDE as one of the two evaluation datasets and reports region-level accuracy and regional bias gap. Dollar Street provides household-object imagery intended to represent geographic and socioeconomic diversity \citep{rojas2022dollarstreet}. Together, these datasets support a research design that evaluates model behavior beyond a single aggregate accuracy value.

\subsection{Dataset Bias and Domain Shift}

Dataset bias has long been recognized as a challenge for visual recognition. \citet{torralba2011datasetbias} show that recognition datasets can contain dataset-specific biases that affect generalization across datasets. Later work on ImageNet generalization and natural distribution shifts similarly suggests that benchmark performance does not fully characterize performance under new data conditions \citep{recht2019imagenet,taori2020naturalshifts}. This literature supports the paper's decision to compare models across datasets and regions rather than relying only on overall object accuracy.

Broader benchmark work also emphasizes the difficulty of real-world distribution shifts. WILDS frames in-the-wild distribution shifts as a recurring challenge across application domains \citep{koh2021wilds}. DomainBed emphasizes careful evaluation design and model-selection choices in domain generalization research \citep{gulrajani2021domainbed}. These papers do not answer this paper's regional-bias question directly, but they provide useful methodological caution: descriptive performance gaps should not be overinterpreted as causal mechanisms.

Visual dataset auditing work is also relevant. REVISE provides tools for measuring and mitigating object-, person-, and geography-related biases in visual datasets \citep{wang2022revise}. This supports the broader idea that geography can be an important axis in visual dataset analysis. TODO: evidence needed to connect REVISE-style dataset auditing more directly to the exact regional metrics used here.

\subsection{GeoDE and Dollar Street}

GeoDE and Dollar Street are central to this paper because they provide regionally meaningful evaluation settings. GeoDE is cited here as the dataset source for geographically diverse object recognition \citep{ramaswamy2023geode}. Dollar Street is cited as the dataset source for household-object imagery designed around geographic and socioeconomic diversity \citep{rojas2022dollarstreet}. Prior Dollar Street object-recognition work provides direct motivation for asking whether models behave unevenly across regions \citep{devries2019object}.

The present draft does not reproduce dataset statistics from the dataset papers because the allowed evidence sources for this draft do not yet include a verified local dataset-statistics table. TODO: evidence needed for local split sizes, region counts, and class counts. TODO: evidence needed for how the local object labels map to the official dataset descriptions.

\subsection{Vision-Language Model Bias and Robustness}

CLIP introduced contrastive language-image pretraining and showed that natural language supervision can produce transferable visual models \citep{radford2021clip}. SigLIP modifies language-image pretraining by using a sigmoid loss over image-text pairs \citep{zhai2023siglip}. These papers support the model descriptions for the vision-language models used in this paper.

For robustness, \citet{fang2022cliprobustness} argue that data distribution is important for distributional robustness in CLIP-like training. This is relevant to the discussion because this paper observes that CLIP and SigLIP do not have identical regional-gap behavior. However, the current experiments do not test pretraining data composition directly. The paper should therefore avoid claims that language-image pretraining causes a particular regional robustness pattern.

\subsection{Self-Supervised Model Robustness}

DINOv2 and MAE provide the main self-supervised model context for this draft. DINOv2 is described as learning robust visual features without supervision \citep{oquab2024dinov2}, while MAE learns visual representations through masked image reconstruction \citep{he2022mae}. In this paper's derived results, MAE has the lowest finetuned regional gap on both datasets, but it does not have the highest object accuracy. This makes self-supervised models important for the accuracy-gap trade-off discussion. The draft should still avoid saying that self-supervision causes lower regional bias, because the evidence is descriptive.

\subsection{CNN and Transformer Backbones}

The evaluated CNN and transformer models are grounded in standard architecture papers. ResNet introduced residual learning for deep convolutional networks \citep{he2016resnet}, and ConvNeXt revisited ConvNet design choices for modern vision architectures \citep{liu2022convnext}. DeiT studied data-efficient training and distillation for vision transformers \citep{touvron2021deit}; Swin introduced shifted-window hierarchical attention \citep{liu2021swin}; and MaxViT introduced a multi-axis attention design \citep{tu2022maxvit}. These citations are used only to describe model families, not to claim anything about their regional bias behavior in this paper.

\subsection{Regional Fairness Metrics and Worst-Group Evaluation}

This paper uses worst-region accuracy and regional bias gap as descriptive metrics. The motivation is related to worst-group evaluation, where average accuracy can hide weak performance for specific groups \citep{sagawa2020groupdro}. ObjectNet and related robustness benchmarks also support evaluation beyond conventional test-set accuracy \citep{barbu2019objectnet}. The regional bias gap used here is simpler than a full fairness analysis, but it helps identify whether high object accuracy is accompanied by uneven regional performance.

