% Draft status: V0
% Evidence status: checked where possible; TODOs mark missing evidence.
\section{Models}

The paper evaluates nine models grouped into four representation paradigms. The grouping is analytical rather than causal: it helps compare architecture families and pretraining signals, but the results alone do not prove that a paradigm causes a particular regional-disparity pattern.

\subsection{Convolutional Vision Paradigm}

The Convolutional Vision Paradigm contains ResNet50 and ConvNeXtV2. ResNet50 is the classical residual CNN baseline, representing the long-standing convolutional approach to image recognition \citep{he2016resnet}. ConvNeXtV2 is a modernized ConvNet that combines convolutional architecture design with representation-learning advances, including masked-autoencoder-inspired training ideas \citep{woo2023convnextv2}. This group tests whether convolutional locality and hierarchical feature extraction remain competitive under geographic shift.

\subsection{Transformer Vision Paradigm}

The Transformer Vision Paradigm contains DeiT3, SwinV2, and MaxViT. DeiT3 is used as a strong supervised Vision Transformer recipe \citep{touvron2022deit3}. SwinV2 is a hierarchical shifted-window transformer designed for scaling capacity and resolution \citep{liu2022swinv2}. MaxViT is a hybrid convolution-attention architecture, but this paper places it under the Transformer Vision Paradigm because its central contribution is multi-axis attention \citep{tu2022maxvit}. This group tests whether attention-based architectures reduce regional sensitivity or primarily improve average recognition.

\subsection{Self-supervised Foundation Paradigm}

The Self-supervised Foundation Paradigm contains DINOv2 and MAE. DINOv2 learns visual features through large-scale self-supervised representation learning \citep{oquab2024dinov2}. MAE learns by reconstructing masked image patches \citep{he2022mae}. These models are useful for the paper because they test whether label-free representation learning transfers more evenly across geographic regions than ordinary supervised recognition pipelines.

\subsection{Vision-Language Foundation Paradigm}

The Vision-Language Foundation Paradigm contains CLIP and SigLIP. CLIP aligns images and text through contrastive language-image pretraining \citep{radford2021clip}. SigLIP uses a sigmoid loss for language-image pretraining \citep{zhai2023siglip}. These models test whether semantic supervision from image-text data improves regional consistency, or whether large-scale language-image pretraining still leaves uneven regional behavior.

\input{revision_model_taxonomy_table}

The taxonomy table describes the intended comparison. The empirical claims in later sections come only from the derived result tables, not from expectations about model families. TODO: reconcile the stored Dollar Street SwinV2 fine-tuning configuration before final submission; the result row is labeled with the paper's intended SwinV2 taxonomy, but one local \texttt{used\_config.yaml} entry requires audit.
