% Draft status: V0
% Evidence status: checked where possible; TODOs mark missing evidence.
\section{Limitations}

This study evaluates only two geographically diverse object-recognition datasets. GeoDE and Dollar Street are highly relevant to the paper's research question, but they cannot represent all forms of geographic, socioeconomic, cultural, environmental, or imaging variation. The results should therefore be interpreted as evidence from two benchmark settings rather than as a universal statement about regional robustness.

The region labels are coarse. GeoDE uses six world-region groups, while the processed Dollar Street subset uses four region groups. These labels may hide country-level, income-level, cultural, linguistic, environmental, and class-composition differences. A model that appears stable across broad regions could still perform unevenly within a region. Conversely, a broad regional gap could reflect several overlapping factors rather than geography alone.

Fine-tuning can depend on dataset split, sample balance, hyperparameters, and model-selection choices. The current fine-tuning protocol is common across the recorded runs, but the paper does not include larger hyperparameter sweeps, alternative model selection, repeated seeds, or uncertainty intervals. The analysis identifies performance disparities, but it cannot prove the causal source of each disparity.

The ImageNet-compatible mapping simplifies the label space. For Dollar Street, the processed experimental subset uses 64 classes rather than the full official 289-category label space. This mapping may exclude objects, merge concepts, or favor categories that align better with ImageNet-style recognition. The very low pretrained accuracies also mean that pretrained geographic-disparity values should be interpreted cautiously.

The selected nine models represent major paradigms but not all possible architectures or foundation models. ResNet50, ConvNeXtV2, DeiT3, SwinV2, MaxViT, DINOv2, MAE, CLIP, and SigLIP are useful representatives, but each paradigm contains many variants. The paper should not claim that a paradigm as a whole is regionally robust or biased based only on this model set.

Finally, the local experimental metadata still needs one audit before a final version. The Dollar Street SwinV2 fine-tuning configuration contains a stored model-key inconsistency that should be reconciled against the actual run provenance. Until that audit is complete, the SwinV2 results should be treated as part of the intended comparison table but not overused for model-specific claims.
