% Draft status: V0
% Evidence status: checked where possible; TODOs mark missing evidence.
\section{Conclusion}

This paper evaluates regional robustness in object recognition using nine models across four representation paradigms: Convolutional Vision, Transformer Vision, Self-supervised Foundation, and Vision-Language Foundation. The evaluation compares ImageNet-pretrained and fine-tuned states on GeoDE and a processed Dollar Street subset, reporting average accuracy together with per-region accuracy and best-minus-worst geographic disparity.

The results show that fine-tuning substantially improves average accuracy for every evaluated dataset-model pair. The strongest fine-tuned model by average accuracy is ConvNeXtV2, which reaches 76.7\% on Dollar Street and 96.6\% on GeoDE. However, the same results show that higher average accuracy does not automatically imply lower geographic disparity. MAE has the lowest fine-tuned disparity on both datasets, even though it is not the highest-accuracy model.

Fine-tuning also changes the regional-disparity picture. In all 18 dataset-model pairs, fine-tuning improves average accuracy and increases the measured best-minus-worst regional gap. This finding should be interpreted cautiously because pretrained evaluations are near the accuracy floor, but it still reinforces the paper's main message: regional behavior must be measured directly. Dollar Street shows larger fine-tuned regional gaps than GeoDE in these experiments, suggesting that dataset design and visual context can strongly affect conclusions about robustness.

At the paradigm level, the Transformer Vision Paradigm has the highest mean fine-tuned accuracy, while the Self-supervised Foundation Paradigm has the lowest mean fine-tuned disparity. These are descriptive patterns, not causal claims. The broader implication is that benchmark progress and average accuracy alone may not reveal uneven model behavior across geographic contexts. Regional robustness should be evaluated directly, with average accuracy, worst-region accuracy, best-region accuracy, and geographic disparity reported together.
